Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2019-04-29 awipev-CO2.Rmd
AT/CT serie from 07-2018 to 11-2018 updated with flags 1
add text to html
RDM updated with new seaFET/durafet measurements

#sfinterv <-sort(unlist(sfinterv, use.names=FALSE))
# set deployment period between 2 spectro measurements.
# add here the new periods sfinterv[..]
d_all <- d_all %>%
  dplyr::mutate(deployment_sf = ifelse(datetime >= sfinterv[1] & datetime <= sfinterv[2], 01, 
                                ifelse(datetime >= sfinterv[2] & datetime <= sfinterv[3], 02, 
                                ifelse(datetime >= sfinterv[3] & datetime <= sfinterv[4], 03, 
                                ifelse(datetime >= sfinterv[4] & datetime <= sfinterv[5], 04,
                                ifelse(datetime >= sfinterv[5] & datetime <= sfinterv[6], 05,
                                ifelse(datetime >= sfinterv[6] & datetime <= sfinterv[7], 06,
                                ifelse(datetime >= sfinterv[7] & datetime <= sfinterv[8], 07,
                                ifelse(datetime >= sfinterv[8] & datetime <= sfinterv[9], 08,
                                ifelse(datetime >= sfinterv[9] & datetime <= sfinterv[10], 09,
                                ifelse(datetime >= sfinterv[10] & datetime <= sfinterv[11], 09, NA )))))))))))

@@

# pH seaFET Final
seafet_contros_xts <- dplyr::select(d_all, datetime, phINT_filtered,pH_s_seafet_temp_field,pHint_tot_sf)
#seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
  #dySeries("voltINT", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>%
  dySeries("phINT_filtered", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>%
  dySeries("pHint_tot_sf", label = "pHT corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 2) %>%
  dySeries("pH_s_seafet_temp_field", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
  dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
  dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>% 
  dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
  dyShading(from =  sfinterv[1], to= sfinterv[2], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[2], to= sfinterv[3], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[3], to= sfinterv[4], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[4], to= sfinterv[5], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[5], to= sfinterv[6], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[6], to= sfinterv[7], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[7], to= sfinterv[8], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[8], to= sfinterv[9], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[9], to= sfinterv[10], color = "#CCCCCC") %>%
   dyShading(from = sfinterv[10], to= sfinterv[11], color = "#E0E0E0") %>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
  dyRangeSelector(height = 30, dateWindow= NULL)

@@

# set deployment period between 2 spectro measurements.
# add here the new periods durinterv[..]
d_all <- d_all %>%
  dplyr::mutate(deployment_dur = ifelse(datetime >= durinterv[1] & datetime <= durinterv[2], 01, 
                                ifelse(datetime >= durinterv[2] & datetime <= durinterv[3], 02, 
                                ifelse(datetime >= durinterv[3] & datetime <= durinterv[4], 03, 
                                ifelse(datetime >= durinterv[4] & datetime <= durinterv[5], 04,
                                ifelse(datetime >= durinterv[5] & datetime <= durinterv[6], 05,
                                ifelse(datetime >= durinterv[6] & datetime <= durinterv[7], 06,
                                ifelse(datetime >= durinterv[7] & datetime <= durinterv[8], 07,
                                ifelse(datetime >= durinterv[8] & datetime <= durinterv[9], 08,
                                ifelse(datetime >= durinterv[9] & datetime <= durinterv[10], 09,
                                ifelse(datetime >= durinterv[10] & datetime <= durinterv[11], 10, NA )))))))))))

@@

# create offset per period + add this offset per period.
d_all <- d_all%>%
 dplyr::mutate(offset_durafet = ifelse(deployment_dur == 1, dat_dur$diff_pH_dur[1],
                                ifelse(deployment_dur == 2, dat_dur$diff_pH_dur[2],
                                ifelse(deployment_dur == 3, dat_dur$diff_pH_dur[3],
                                ifelse(deployment_dur == 4, dat_dur$diff_pH_dur[4],
                                ifelse(deployment_dur == 5, dat_dur$diff_pH_dur[5],
                                ifelse(deployment_dur == 6, dat_dur$diff_pH_dur[6],
                                ifelse(deployment_dur == 7, dat_dur$diff_pH_dur[7],
                                ifelse(deployment_dur == 8, dat_dur$diff_pH_dur[8],
                                ifelse(deployment_dur == 9, dat_dur$diff_pH_dur[9],
                                ifelse(deployment_dur == 10, dat_dur$diff_pH_dur[10], 0)))))))))),
              pH_durafet_corrected = pH_durafet + offset_durafet
              )
# DURAFET 
durafet_contros_xts <- dplyr::select(d_all, datetime, pH_durafet, pH_s_durafet_temp_field,pH_durafet_corrected)
durafet_contros_xts <- as.xts(durafet_contros_xts, order.by = d_all$datetime)
 dygraph(durafet_contros_xts, group = "awipev", main="pH durafet (in Ferrybox)", ylab="pHT") %>%
    dySeries("pH_durafet", label = "Raw durafet pH", color ="blue", strokeWidth=0, pointSize=2) %>%
    dySeries("pH_durafet_corrected", label = "pH durafet corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 2 ) %>%
    dySeries("pH_s_durafet_temp_field", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
    dyEvent(as.POSIXct("2017-10-30 13:00:00", tz="GMT"), "New holder installed", labelLoc = "bottom", color="red") %>% 
    dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "durafet installed", labelLoc = "bottom", color="red") %>%
    # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
    dyShading(from =  durinterv[1], to= durinterv[2], color = "#CCCCCC") %>%
    dyShading(from = durinterv[2], to= durinterv[3], color = "#E0E0E0") %>%
    dyShading(from = durinterv[3], to= durinterv[4], color = "#CCCCCC") %>%
    dyShading(from = durinterv[4], to= durinterv[5], color = "#E0E0E0") %>%
    dyShading(from = durinterv[5], to= durinterv[6], color = "#CCCCCC") %>%
    dyShading(from = durinterv[6], to= durinterv[7], color = "#E0E0E0") %>%
   dyShading(from = durinterv[7], to= durinterv[8], color = "#CCCCCC") %>%
   dyShading(from = durinterv[8], to= durinterv[9], color = "#E0E0E0") %>%
   dyShading(from = durinterv[9], to= durinterv[10], color = "#CCCCCC") %>%
   dyShading(from = durinterv[10], to= durinterv[11], color = "#E0E0E0") %>%
    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
    dyRangeSelector(height = 30, dateWindow= NULL)

@@

- 2015-11-18
- 2016-07-28
- 2016-09-29
- 2016-11-17
- 2016-11-23
- 2016-12-29
- 2017-01-19
- 2017-05-04
- 2018-04-26
- 2018-05-04
- 2018-05-16
- 2018-05-25
- 2018-06-22
- 2018-06-30
- 2018-07-27

@@

- 2015-08-06
- 2015-08-13
- 2016-05-12
- 2016-05-16
- 2016-06-16
- 2016-07-28
- 2016-09-08
- 2016-10-27
- 2016-11-17
- 2017-01-19
- 2017-03-02
- 2017-04-27
- 2017-09-17
- 2018-04-26
- 2018-05-04
- 2018-05-12
- 2018-05-25
- 2018-06-30

>>>>

#sfinterv <-sort(unlist(sfinterv, use.names=FALSE))
# set deployment period between 2 spectro measurements.
# add here the new periods sfinterv[..]
d_all <- d_all %>%
  dplyr::mutate(deployment_sf = ifelse(datetime >= sfinterv[1] & datetime <= sfinterv[2], 01, 
                                ifelse(datetime >= sfinterv[2] & datetime <= sfinterv[3], 02, 
                                ifelse(datetime >= sfinterv[3] & datetime <= sfinterv[4], 03, 
                                ifelse(datetime >= sfinterv[4] & datetime <= sfinterv[5], 04,
                                ifelse(datetime >= sfinterv[5] & datetime <= sfinterv[6], 05,
                                ifelse(datetime >= sfinterv[6] & datetime <= sfinterv[7], 06,
                                ifelse(datetime >= sfinterv[7] & datetime <= sfinterv[8], 07,
                                ifelse(datetime >= sfinterv[8] & datetime <= sfinterv[9], 08,
                                ifelse(datetime >= sfinterv[9] & datetime <= sfinterv[10], 09,
                                ifelse(datetime >= sfinterv[10] & datetime <= sfinterv[11], 10,
                                       ifelse(datetime >= sfinterv[11] & datetime <= sfinterv[12], 11,
                                              ifelse(datetime >= sfinterv[12] & datetime <= sfinterv[13], 12,
                                                     ifelse(datetime >= sfinterv[13] & datetime <= sfinterv[14], 13,NA ))))))))))))))

@@

# pH seaFET Final
seafet_contros_xts <- dplyr::select(d_all, datetime, phINT_filtered,pH_s_seafet_temp_field,pHint_tot_sf)
#seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
  #dySeries("voltINT", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>%
  dySeries("phINT_filtered", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>%
  dySeries("pHint_tot_sf", label = "pHT corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 2) %>%
  dySeries("pH_s_seafet_temp_field", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
  dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
  dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>% 
  dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
  dyShading(from =  sfinterv[1], to= sfinterv[2], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[2], to= sfinterv[3], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[3], to= sfinterv[4], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[4], to= sfinterv[5], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[5], to= sfinterv[6], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[6], to= sfinterv[7], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[7], to= sfinterv[8], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[8], to= sfinterv[9], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[9], to= sfinterv[10], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[10], to= sfinterv[11], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[11], to= sfinterv[12], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[12], to= sfinterv[13], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[13], to= sfinterv[14], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[14], to= sfinterv[15], color = "#E0E0E0") %>%

  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
  dyRangeSelector(height = 30, dateWindow= NULL)

@@

# set deployment period between 2 spectro measurements.
# add here the new periods durinterv[..]
d_all <- d_all %>%
  dplyr::mutate(deployment_dur = ifelse(datetime >= durinterv[1] & datetime <= durinterv[2], 01, 
                                ifelse(datetime >= durinterv[2] & datetime <= durinterv[3], 02, 
                                ifelse(datetime >= durinterv[3] & datetime <= durinterv[4], 03, 
                                ifelse(datetime >= durinterv[4] & datetime <= durinterv[5], 04,
                                ifelse(datetime >= durinterv[5] & datetime <= durinterv[6], 05,
                                ifelse(datetime >= durinterv[6] & datetime <= durinterv[7], 06,
                                ifelse(datetime >= durinterv[7] & datetime <= durinterv[8], 07,
                                ifelse(datetime >= durinterv[8] & datetime <= durinterv[9], 08,
                                ifelse(datetime >= durinterv[9] & datetime <= durinterv[10], 09,
                                ifelse(datetime >= durinterv[10] & datetime <= durinterv[11], 10, 
                                ifelse(datetime >= durinterv[11] & datetime <= durinterv[12], 10,
                                ifelse(datetime >= durinterv[12] & datetime <= durinterv[13], 10,NA )))))))))))))

@@

# create offset per period + add this offset per period.
d_all <- d_all%>%
 dplyr::mutate(offset_durafet = ifelse(deployment_dur == 1, dat_dur$diff_pH_dur[1],
                                ifelse(deployment_dur == 2, dat_dur$diff_pH_dur[2],
                                ifelse(deployment_dur == 3, dat_dur$diff_pH_dur[3],
                                ifelse(deployment_dur == 4, dat_dur$diff_pH_dur[4],
                                ifelse(deployment_dur == 5, dat_dur$diff_pH_dur[5],
                                ifelse(deployment_dur == 6, dat_dur$diff_pH_dur[6],
                                ifelse(deployment_dur == 7, dat_dur$diff_pH_dur[7],
                                ifelse(deployment_dur == 8, dat_dur$diff_pH_dur[8],
                                ifelse(deployment_dur == 9, dat_dur$diff_pH_dur[9],
                                ifelse(deployment_dur == 10, dat_dur$diff_pH_dur[10], 
                               ifelse(deployment_dur == 11, dat_dur$diff_pH_dur[11],
                                ifelse(deployment_dur == 12, dat_dur$diff_pH_dur[12],0)))))))))))),
              pH_durafet_corrected = pH_durafet + offset_durafet
              )
# DURAFET 
durafet_contros_xts <- dplyr::select(d_all, datetime, pH_durafet, pH_s_durafet_temp_field,pH_durafet_corrected)
durafet_contros_xts <- as.xts(durafet_contros_xts, order.by = d_all$datetime)
 dygraph(durafet_contros_xts, group = "awipev", main="pH durafet (in Ferrybox)", ylab="pHT") %>%
    dySeries("pH_durafet", label = "Raw durafet pH", color ="blue", strokeWidth=0, pointSize=2) %>%
    dySeries("pH_durafet_corrected", label = "pH durafet corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 2 ) %>%
    dySeries("pH_s_durafet_temp_field", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
    dyEvent(as.POSIXct("2017-10-30 13:00:00", tz="GMT"), "New holder installed", labelLoc = "bottom", color="red") %>% 
    dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "durafet installed", labelLoc = "bottom", color="red") %>%
    # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
    dyShading(from =  durinterv[1], to= durinterv[2], color = "#CCCCCC") %>%
    dyShading(from = durinterv[2], to= durinterv[3], color = "#E0E0E0") %>%
    dyShading(from = durinterv[3], to= durinterv[4], color = "#CCCCCC") %>%
    dyShading(from = durinterv[4], to= durinterv[5], color = "#E0E0E0") %>%
    dyShading(from = durinterv[5], to= durinterv[6], color = "#CCCCCC") %>%
    dyShading(from = durinterv[6], to= durinterv[7], color = "#E0E0E0") %>%
   dyShading(from = durinterv[7], to= durinterv[8], color = "#CCCCCC") %>%
   dyShading(from = durinterv[8], to= durinterv[9], color = "#E0E0E0") %>%
   dyShading(from = durinterv[9], to= durinterv[10], color = "#CCCCCC") %>%
   dyShading(from = durinterv[10], to= durinterv[11], color = "#E0E0E0") %>%
    dyShading(from = durinterv[11], to= durinterv[12], color = "#CCCCCC") %>%
    dyShading(from = durinterv[12], to= durinterv[13], color = "#E0E0E0") %>%
   dyShading(from = durinterv[13], to= durinterv[14], color = "#CCCCCC") %>%
    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
    dyRangeSelector(height = 30, dateWindow= NULL)

@@

- 2015-11-18
- 2016-07-28
- 2016-09-29
- 2016-11-17
- 2016-11-23
- 2016-12-29
- 2017-01-19
- 2017-05-04
- 2017-08-31
- 2018-04-26
- 2018-05-04
- 2018-05-16
- 2018-05-25
- 2018-06-22
- 2018-06-30
- 2018-07-27
- 2018-07-20
- 2018-08-03
- 2018-08-10
- 2018-08-24
- 2018-08-31
- 2018-09-07
- 2018-09-14
- 2018-09-21
- 2018-09-28
- 2018-10-05
- 2018-10-12
- 2018-10-19
- 2018-10-26
- 2018-11-02
- 2018-11-09
- 2018-11-16
- 2018-11-23

@@

- 2015-08-06
- 2015-08-13
- 2016-05-12
- 2016-05-19
- 2016-06-16
- 2016-07-28
- 2016-09-08
- 2016-10-27
- 2016-11-17
- 2017-01-19
- 2017-03-02
- 2017-04-27
- 2017-09-14
- 2018-04-26
- 2018-05-04
- 2018-05-12
- 2018-05-25
- 2018-06-30
- 2018-07-20
- 2018-08-03
- 2018-08-31
- 2018-09-07
- 2018-09-14
- 2018-09-28
- 2018-10-05
- 2018-10-12
- 2018-10-19
- 2018-10-26
- 2018-11-02
- 2018-11-09
- 2018-11-16
- 2018-11-23
